Proposed Solution

### 2015-12-12 proposedSolution.tex
starting some examples
writing pseduocode

usertime :: (RuleSet,a) -> ConfigFile a -> Maybe Error
usertime r c =
  d = convert c
  e = verifyOn r d
  return e
\end{lstlisting}

@@

@@

\subsection{Format - Syntax}
This problem is exemplified in box (b) and (c) of the image.
These are ordering/dependency errors and require analysis over multiple lines.
Looking for substrings over lines can solve (b).
Not sure about (c)

@@

>>>>

usertime :: (RuleSet,a) -> ConfigFile a -> Maybe Error
usertime r c =
  d = convert c
  e = verifyOn r d
  return e

data RuleSet = {Lexical = [Clause], Syntax = [Clause], Value = [Clause]}
\end{lstlisting}

@@

\begin{lstlisting}
learnOn :: [ConfigFile Common] -> RuleSet
learnOn cs = 
  rs = map genConstraints cs
  foldl1 mergeRules rs

genConstraints :: ConfigFile Common -> RuleSet
genConstraints c =
  r1 = learnLexicalConstraints c
  r2 = learnSyntaxConstraints c
  r3 = learnValueConstraints c
  return RuleSet {r1, r2, r3}

mergeRules :: RuleSet -> RuleSet -> RuleSet
mergeRules rs rs' =
  return RuleSet
    { mergeLex (Lexical rs) (Lexical rs')
    , mergeSyn (Syntax rs)  (Syntax rs')
    , mergeVal (Value rs)   (Value rs')}
\end{lstlisting}

@@

\begin{lstlisting}
learnLexicalConstraints :: ConfigFile Common -> [Clause]
learnLexicalConstraints =

mergeLex =
  strisynth?
\end{lstlisting}

\subsection{Format - Syntax}
This problem is exemplified in box (b) and (c) of the image.
These are ordering/dependency errors and require analysis over multiple lines.

\begin{lstlisting}
learnSyntaxConstraints :: ConfigFile Common -> [Clause]
learnSyntaxConstraints c =
  ls = lines c
  concatMap (makeOrderPairs ls) ls

makeOrderPairs :: [Text] -> Text -> [(Text,Text)]
makeOrderPairs ls l = 
  map (,l) ls

mergeSyn :: [Clause] -> [Clause] -> [Clause]
mergeSyn curr new =
  combined = intersect curr new
  return combined
\end{lstlisting}

@@

\begin{lstlisting}
learnValueConstraints :: Config Common -> RuleSet
learnValueConstraints c =
  ls = lines cs
  tys = seperateValsOnType ls :: [(Type,Text)]
  concatMap (makeRelations tys) tys

makeRelations :: [(Type,Text)] -> (Type,Text)
makeRelations ts (ty,tx) =
  map (f (ty,tx)) ts
  f (ty,tx) (ty',tx') = if ty==ty' then synthesizeComparison ty tx tx' else []

synthesizeComparison :: Type -> Text -> Text -> Clause
synthesizeComparison Int t t' =
  if t<t' then "t<t'"
  if t==t' then "t==t'"
  ...
synthesizeComparison String t t' =
synthesizeComparison IP t t' =
...

mergeVal rs rs' = 
\end{lstlisting}
